Learning Augmented Joint-Space Task-Oriented Dynamical Systems: \\ A Linear Parameter Varying and Synergetic Control Approach

### 2017-10-30 paper/main_RA-L_v1_merge.tex
Merged Yo and my re-writes.. need to get rid of 3 columns!

\IEEEpeerreviewmaketitle
\section{Introduction}
\label{sec:intro}
\textcolor{red}{We'll remove the subsection headings later..\\ Some comments:\\- Change PbD to LfD everywhere}
\subsection{\textcolor{red}{Motivation for learning joint+task-space behaviors}}
\textcolor{red}{*See comments in tex*}
% % TO YO: OUTLINE FOR RE-WRITING THIS PART
%1. Start with motivation of LfD  
%2. Mention that we can learn behaviors in either joint or task space 
%3. briefly summarize the approaches in each without going into detail; i.e. probabilistic models, DS, etc 
%4. Motivate why we want to learn behaviors in joint+task space: 1 is because of the implications of IK as we already discuss, 2 to mimic joint trajectories.. here give your example of why we would want that and mention applications such as table tennis[1], grasping[2] and bi-manual coordination [3].
%
%[1] Y. Huang, D. B ̈uchler, O. Koc, B. Scholkopf and J. Peters, “Jointly
%learning trajectory generation and hitting point prediction in robot table
%tennis,” in Proc. IEEE International Conference on Humanoid Robots,
%2016, pp. 650-655.
%
%[2] S. Calinon and A. Billard, “Statistical learning by imitation of competing constraints in joint space and task space,” Advanced Robotics,vol. 23, pp. 2059-2076, 2009.
%
%[3] J. Silverio, S. Calinon, L. Rozo and D. G. Caldwell, “Learning competing constraints and task priorities from demonstrations of bimanual skills,” arXiv:1707.06791, 2017.

Robot motion planning in joint-space has long been a major field of study \cite{kelly2006control}. For manipulation problems with an objective defined in task space (i.e. target or desired trajectory), we can often find a myriad of joint-space trajectories to achieve the same task-space goal. In many cases, however, certain joint-space trajectories are favored over others; for example, when we expect the robot to follow a desired joint-space behavior or ``style", as illustrated in Fig. \ref{fig:robot_example}.

Learning robot motion generators that follow desired joint and/or task-space behaviors is, in fact, the central focus of Programming by Demonstration (PbD) \cite{billard2008robot} \cite{Argall:RAS:2009}. Historically, much of the original work in PbD focused on learning motions solely in joint-space by parameterizing motions using GMMs \cite{Calinon:HRI:2007}, HMMs \cite{Garrido:Neuro:2015}, GPs \cite{Shon:HUM:2005}, or other probabilistic models \cite{Schaal:IROS:2003,Schaal:AI:2002}. Concurrently, a significant body of work from the graphics community was targeted at learning joint-space motion ``styles" from human motion capture data, through a variety of latent-space and stylistic probabilistic motion models \cite{gielniak2010stylized,grochow2004style}. Yet, over time, research shifted to pure task-space learning \cite{Pastor:ICRA:2009,Gribovskaya:IJRR:2011,Calinon:ISR:2015}, which has two main advantages over pure joint-space: \textit{generalization} and \textit{re-usability}. By learning motions in task-space, one can concisely encode the task-relevant features and generate new motions which meet these task-space criteria. Furthermore, a task-space trajectory is robot-independent, and thus can be reused across robots with differing morphologies.

A major drawback of these initial task-space methods was that despite learning motions similar to the demonstrations, there was no guarantee when applying the learned motion to a new problem (e.g. a different initial/target position) that the end-effector would stably converge to its ultimate task-space target. This led to the introduction and subsequent popularity of task-space learning techniques such as SEDS \cite{khansari2011learning}, $\tau$-SEDS \cite{Neumann:RAS:2015}  and LMDS \cite{Kronander:RAS:2015} which encode task-space behaviors as asymptotically stable dynamical systems (DS) guaranteed to converge towards a desired task-space target.

@@

For all the previously mentioned task-space techniques, the robot is ultimately controlled by projecting the desired task-space velocity into joint-space via Jacobian Pseudo-Inverse based Inverse-Kinematic (IK) approximations and variants thereof \cite{kelly2006control}. When the main focus is on executing a complex task-space behavior, regardless of a specific joint-space constraint, this approach has been deemed sufficient \cite{figueroa2016HRIrolling,ureche2015taskconst}. However, for other applications, such an approach yields significant problems \cite{buss2004introduction}. First of all, finding the pseudo-inverse is computationally taxing. Moreover, when the Jacobian matrix cannot be inverted (i.e. when the robot is near a singularity) its behavior becomes erratic, requiring layers of additional engineering to generate smooth trajectories and ensure the desired task-space behavior. These problems encapsulate the main source of inaccuracies in tasks that require generating fast dynamical motions, such as catching or reaching for moving objects \cite{7439839,Salehian-RSS-16}.

Although DS-based task-space learning techniques ensure target convergence and stability, they still suffer from this reliance on IK methods, possibly generating erratic or discontinuous motions during execution. Further, for certain tasks, rather than generating arbitrary joint-space trajectory returned by the IKs solver, it might be desirable to learn behaviors and ``styles" in joint-space directly.  For example, throwing a ball is a motion less characterized by task-space behaviors (the ball moving backwards and then forwards) and more characterized by the joint behaviors: the elbow folds, the shoulder moves back and then swings forward, followed by the elbow straightening and the wrist snapping down. For a visual example of the need for such combined task/joint-space behavior learning, see Fig. \ref{fig:robot_example}. This is precisely the shortcoming associated with LfD in task-space: it fails to learn the joint-space behavior of the system. The current formulation of the DS-based learning techniques introduced thus far (e.g. SEDS, $\tau$-SEDS LMDS, etc.) do not allow for integrating combined task/joint-space behavior learning.

\subsection{\textcolor{red}{Approaches that tackle the joint+task problem}}
\textcolor{red}{*See comments in tex*}
% TO YO:
% ADD THESE THREE REFERENCES HERE AND SUMMARIZE THEM
%[1] Y. Huang, D. B ̈uchler, O. Koc, B. Scholkopf and J. Peters, “Jointly
%learning trajectory generation and hitting point prediction in robot table
%tennis,” in Proc. IEEE International Conference on Humanoid Robots,
%2016, pp. 650-655.
%
%[2] S. Calinon and A. Billard, “Statistical learning by imitation of competing constraints in joint space and task space,” Advanced Robotics,vol. 23, pp. 2059-2076, 2009.
%
%[3] J. Silverio, S. Calinon, L. Rozo and D. G. Caldwell, “Learning competing constraints and task priorities from demonstrations of bimanual skills,” arXiv:1707.06791, 2017.

\cite{calinon2008probabilistic} notably attempted to address this problem by learning separate motion policies in task space and the null space of the Jacobian (which would not affect task-space position), and driving the robot with a weighted sum of the two. However, this approach no longer guarantees convergence to the desired task-space target and is still reliant on computing the pseudo-inverse Jacobian.

\cite{lee2014unifying} learns from demonstration in both joint and task space within the "thin-plate spline" trajectory warping framework, but does not propose a dynamical system for generating motions.

\subsection{Our proposed Approach}
\textcolor{red}{Dynamical System, Why?\\Linear Parameter Varying, Why?\\Lower-Dimensional Manifold, Why?\\}
In this work, we seek to devise an augmented \textbf{J}oint-space \textbf{T}ask-oriented \textbf{D}ynamical \textbf{S}ystem (JT-DS) that not only incorporates task-space attractors, but also avoids the problems generated by pseudo-inverse approximations. \cite{hersch2008reaching} proposed an approach with similar properties to this desiderata, where two concurrent DS, one in task-space and one in joint-space, are modulated by enforcing kinematic coherence constraints to avoid singularities. The resulting DS avoids singularities through generalization of the pseudo-inverse approximations. However, because the two DS have their own unique attractors, the non-linear interaction between them imposed by the kinematic constraints does not ensure that the combined DS has a unique attractor. This gives rise to spurious attractors or cycles, and thus must be carefully tuned in order to avoid them. In this work, we depart from any modulation or combination of DS and instead propose a novel dynamical system which:

\begin{enumerate}[leftmargin=*]
\item computes a \begin{bf}complex motion in joint space\end{bf} that provably and stably converges to a \begin{bf}fixed task-space target\end{bf}.
\item \textbf{avoids} the need for computing \textbf{pseudo-inverses}, and cleanly moves through kinematic ``singularities".
\item is formulated such that complex \textbf{joint-space behaviors} can be \textbf{learned} from demonstrations in \textbf{synergy space}.
\end{enumerate}

The most similar approach to our proposed DS is the Jacobian transpose (JT) control \cite{wolovich1984computational} method. JT control is an inverse kinematics
method that yields a dynamical system in joint space $\dot{q} = f(q)$ which converges stably (in the sense of Lyapunov) over time to a desired end-effector position $x^*$, without the need for pseudo-inverse computations. It shares some of our approach's advantages: fast computation and provable task-space stability. However, despite some previous work designing velocity adjustments by hand \cite{Shi2016}, this is the first known work to employ a JT system to learn behaviors from demonstrations. 
%while obeying the robots kinematic constraints.

This paper is organized as follows. Section \ref{Sec:Prob} formalizes the problem. The proposed dynamical system is introduced in Section \ref{Sec:DS}. In Section \ref{Sec:Learning}, a probabilistic model is introduced to approximate the parameters of the dynamical system. In addition, a convex optimization problem is  formalized to estimate these parameters. The effectiveness of the proposed method is shown through simulations and experiments on a 7-DOF robot-arm in Section \ref{Sec:Exp}. The paper is finalized with a discussion over our method and results in Section \ref{Sec:Dis}.

%\begin{figure}[t]
%\centering
%\includegraphics[width=0.95\linewidth,trim={0 20 450 0},clip]{Pic/Schematic.jpg}
%\includegraphics[width=0.9\linewidth,trim={580 20 0 0},clip]{Pic/Schematic.jpg}
%\caption{ Standard control architecture using Cartesian dynamical systems (DS)\textbf{(top)}  and our proposed approach \textbf{(bottom)}.}
%\label{fig:schematic}
%\end{figure}
\section{Problem Statement} \label{Sec:Prob}
Consider a robotic system with $d$ task-space dimensions and $m$ degrees of freedom. We direct the system using a joint position or joint velocity controller, which can have joint position limits and a maximum joint velocity. We are further provided with a set of $N$ demonstrated joint-space trajectories $D=\{\{q_{t,n},\dot{q}_{t,n}\}_{t=1,\dots, T_n}\}_{n=1,\dots,N}$, where $T_n$ is the number of the sample points of the $n^{\text{th}}$ demonstration. We refer to the system's joint-space position as $q=\begin{bmatrix} q^1 & \dots & q^m
\end{bmatrix}^T \in \mathbb{R}^m$, and to its task-space position as $x\in \mathbb{R}^d$.\footnote{For sake of brevity and simplicity, the time index, $t$, is dropped throughout the paper. } The kinematics of the robot are assumed to be known, hence, the robot's forward kinematics is indicated by $x = H(q)$ and its Jacobian is $J(q) = \frac{dx}{dq}\in \mathbb{R}^{m\times d}$.\\
We wish to formulate a dynamical system $\dot{q} = f(q)$ which satisfies the following two criteria:
\renewcommand{\labelenumi}{(\Roman{enumi})}
\begin{enumerate}
\item The dynamical system must be Lyapunov stable\footnote{Unless otherwise specified, "stability" in this paper always refers to global Lyapunov stability. We make no claim to proving global asymptotic stability, which is in fact impossible to achieve in a joint-constrained kinematic system. For example, any finite-size manipulator will always have regions beyond its reach that it cannot converge to.} with respect to a fixed task-space target $x^*$. This can be expressed by ensuring that the following Lyapunov function
\begin{equation}
V(q) = (H(q) - x^*)^TP(H(q) - x^*) 
\label{eq:Lyp}
\end{equation}
is stable; i.e. $\dot{V}(q)\leq0 ~\forall q\in Q$ and $V(q)=0~ \forall q\in Q^*$. Where  $Q=\{q|q^i_{min} < q^i < q^i_{max},~\forall i\in \{1,\dots,d\}\}$ and $Q^*=\{q|H(q)=x^*\wedge q\in Q\}$. $P\in \mathbb{R}^{d\times d} $ is a symmetric and positive definite matrix. $V(.)$ can be thought of as a metric for the task-space distance-to-go.
\item The dynamical system should encapsulate the desired joint-space behaviors such that the following metric is minimized
\begin{equation}
\vspace{-5pt}
e_{total} = \frac{1}{NT_n}\sum_{n=1}^N\sum_{t=0}^{T_n} \left \| \dot{q}_{d; t,n} - f(q_{t,n}) \right \|
\label{eq:optim_error}
\end{equation}
  where $\dot{q}_d$ is the desired ``true" velocity, and $f(\cdot)$ is the motion generation policy.
\end{enumerate}

%Lastly, we wish to capture joint-space behaviors in our dynamical system.
We make two decisions by the choice of behavior error metric \eqref{eq:optim_error}. First, the metric implicitly suggests that behaviors are defined by expert motions of the behavior, and that fulfilling a behavior means moving similarly to the experts' motion. Second, the type of feature of the trajectory that is being minimized is important. If instead the error feature were joint position distance $\sum_i\left \| q_{d,i} - q_i \right \|$ where $q_d$ is a vector of demonstrated positions, then executing a "behavior" would imply mimicking position, but not velocity. Alternatively, if the error feature were joint velocity direction $\sum_i \left | \frac{\dot{q}_{d,i}}{\left \| \dot{q}_{d,i} \right \|} - \frac{\dot{q}_i}{\left \| \dot{q}_i \right \|} \right |$ mimicking a "behavior" would involve following the motion profile, but not the motion's speed (so for example a slap and a push would exhibit the same behavior). By choosing the combined direction and magnitude of the joint velocity as the error, we are choosing to mimic the magnitude and direction of the motion, which \cite{gielniak2010stylized} suggests is visually most similar to the human definition of "joint motion style".
\section{Augmented \textbf{J}oint-Space \textbf{T}ask-oriented \textbf{D}ynamical \textbf{S}ystem} \label{Sec:DS}
\label{sec:proposed_system}
\textcolor{red}{Change semi-definite to definite everywhere\\Change overall $A(q)$ to $\mathcal{A}(q)$\\ Introduce 'behavior synergies' here\\}
We propose the following augmented Joint-space Task-oriented Dynamical System (JTDS) to achieve the two criteria presented in \ref{eq:Lyp} and \ref{eq:optim_error}.
\begin{equation}
\label{eq:ds}
\dot{q} = f(q) = -A(q)J^T(q)P(H(q) - x^*)
\end{equation}
where $P\in \mathbb{R}^{d\times d}$, and $A(q)\in \mathbb{R}^{m\times m}$ is constructed using the Linear Parameter Varying system paradigm \cite{emedi2016fixed,7439839}, where the overall $A(q)$ is a changing linear combination of constant  matrices, each of which encodes a local joint-space synergy. 
\begin{equation}
\label{eq:A_def}
A(q) = \sum_{k=1}^{K}\theta_k(q)A_k 
\end{equation}
where $A_k\in \mathbb{R}^{m\times m} $ are the different synergies and $\theta_k(q)\in \mathbb{R}^{1}~\forall k\in\{1,\dots,K\} $ are the scheduling parameters\footnote{The scheduling parameters can be a function of time $t$, the states of the
system $q $ or external signals $d(t)$, i.e. $\theta_k (t, q(t), d(t))$. In this paper, we only consider it as a function of the states of the system. It is noteworthy that the presented stability proof can easily be extended for $\theta_k (t, q(t), d(t))$.} modulating each local synergy through time as well as space. Based on \eqref{eq:ds}, one can utilize different synergies in different regions, and compose them to create a more complex multi-behavior motion.

\begin{figure}[t]
\centering
\includegraphics[width=\linewidth]{Pic/A_comparison_positions.pdf}
\caption{Three example 3-DOF motions (A, B, C), each with a different constant joint augmentation matrix $A$ (emphasizing the hip, knee, and ankle respectively), A: $A(q)=diag(5,1,1) $, B: $A(q)=diag(1,5,1)$, and C: $A(q)=diag(1,1,5)$. On the left, the task-space traces of each motion. On the right, the time-scaled joint positions of each joint. Each motion tends to use its ``primary" joint most and uses the other available joints to compensate for what the primary joint cannot do.}
\label{fig:A_example}
\vspace{-15pt}
\end{figure}

Before proving that the proposed dynamical system satisfies all of the criteria, let us establish an intuitive understanding of the components of the system. While it may seem daunting at first, each of the elements has a straightforward explanation. One can intuitively understand the control law as follows: $(H(q) - x^*)$ denotes the position error w.r.t. the task target (warped according to P), and by multiplying that error by the transposed Jacobian $J^T(q)$, the error is projected into joint space (similar to Jacobian transpose control \cite{wolovich1984computational,sciavicco1988solution}). The positive semi-definite matrix $A(q)$ warps the resulting joint-space velocity; Fig. \ref{fig:A_example} illustrates the effects of  $A(q)$ on the generated motion. Thus the controller can be thought of as a proportional controller in joint space. Lastly, we refer to the $P$ matrix as the \begin{bf} task augmentation matrix \end{bf}(because it augments the task error, and thus the direction of motion) and $A(q)$ as the \begin{bf} joint augmentation matrix \end{bf} (because it augments the outputted joint velocities).
%When using each of these matrices, the controller will augment the joint velocities to favor using one joint more than the others (in $A_1$ the hip, in $A_2$ the knee, and in $A_3$ the ankle). This ''augmentation" is simply a matrix multiplication ($A\dot{q}_{raw}$). The components of the outputted velocity are linear combinations of the ''raw" un-augmented joint velocities, where the entries in $A$ define the precise ratios. We can see the joint positions resulting from our experiment over time on the right side of Fig. \ref{fig:A_example}. Each motion tends to use its ``primary" joint most (the joint where the velocity is heavily scaled up) and uses the other available joints to compensate for what the primary joint cannot do. For example, Motion 1 starts out using mostly the hip, but once moving the hip no longer brings the system closer to the goal, the system uses the other joints to fold inwards and reach the goal. Ultimately, all three controllers converge on their target, but each has a different path through joint space depending on which joints we choose to emphasize in the behavior matrix $A$. The off-diagonal terms of $A$ have a more nuanced contribution; e.g. $A_{1,2}$ defines the amount that elbow velocity should be converted into hip velocity.

@@

%By learning a position-dependent joint augmentation matrix $A(q)$, we are able to execute the joint behaviors discussed earlier by augment the relative velocities of our joints. \eqref{eq:A_def} constructs our overall $A(q)$ as a linear combination of $A_k~\forall k\in\{1,\dots,K\}$ (each weighted by $\theta_k(q)$), where one can enforce different local joint behaviors in different regions, and compose them to create a more complex multi-behavior motion. In this paper the joint behavior matrix $A(q)$ is determined using only the joint position $q$, though one could potentially use other information such as joint velocity $\dot{q}$, environment force or target task position $x^*$.\\

\section{Learning \textbf{J}oint-Space \textbf{T}ask-oriented \textbf{D}ynamical \textbf{S}ystem} 
\label{Sec:Learning}

>>>>

\IEEEpeerreviewmaketitle
\section{Introduction}
\label{sec:intro}
Robot motion planning in joint-space has long been a major field of study \cite{kelly2006control}. For manipulation problems with an objective defined in task space (i.e. target or desired trajectory), we can often find a myriad of joint-space trajectories to achieve the same task-space goal. In many cases, however, certain joint-space trajectories are favored over others; for example, when we expect the robot to follow a desired joint-space behavior or ``style", as illustrated in Fig. \ref{fig:robot_example}. In this paper, we will explore the problem of learning a preferred joint-space behavior from previously demonstrated trajectories while still accomplishing a task-space goal, through the Learning from Demonstrations (LfD) paradigm \cite{billard2008robot,Argall:RAS:2009}.

Many LfD approaches learn motions in either joint space \cite{Calinon:HRI:2007, Garrido:Neuro:2015, Schaal:IROS:2003,Schaal:AI:2002} or task space \cite{Pastor:ICRA:2009,Gribovskaya:IJRR:2011,Calinon:ISR:2015}. These approaches generally learn probabilistic model of the demonstrated motions, and construct a dynamical system that chooses behaviors according to the learned model.
Both joint and task space are independently useful: joint-space behaviors let us directly influence the behavior of the physical robot, while task-space behaviors let us control the most task-relevant component of the robot's behavior. In particular, a number of approaches have pioneered stable convergence to an attractor in task space \cite{khansari2011learning, Neumann:RAS:2015, Kronander:RAS:2015} as a desirable capability for a dynamical system.

In many cases, one may want to specify a joint-space behavior while simultaneously fulfilling a task-space objective. For example, throwing a ball is a motion characterized both by a task-space behavior (the ball moves backwards and then forwards) and also more obviously by its joint-space behavior (the elbow folding, the shoulder moving back and then swinging forward, and then the elbow straightening and the wrist snapping down). Similarly, learned joint-space behaviors are helpful in playing ping-pong \cite{huang2016jointly}, grasping \cite{calinon2010learning}, and avoiding self-collisions of bi-manual manipulators \cite{silverio2017learning}. For a visual example of a task-space problem in which joint behavior is essential, see Fig. \ref{fig:robot_example}.

@@

Furthermore, learning a motion in joint space allows us to avoid inverse kinematic (IK) approximations. The previously discussed task-space dynamical systems all rely on projecting the desired task-space velocity into joint-space via Jacobian Pseudo-Inverse based Inverse-Kinematic (IK) approximations and variants thereof \cite{kelly2006control}. When the main focus is on executing a complex task-space behavior, regardless of a specific joint-space constraint, this approach has been deemed sufficient \cite{figueroa2016HRIrolling,ureche2015taskconst}. However, for other applications, such an approach yields significant problems \cite{buss2004introduction}. First of all, finding the pseudo-inverse is computationally taxing. Moreover, when the Jacobian matrix cannot be inverted (i.e. when the robot is near a singularity) its behavior becomes erratic, requiring layers of additional engineering to generate smooth trajectories and ensure the desired task-space behavior. These problems encapsulate the main source of inaccuracies in tasks that require generating fast dynamical motions, such as catching or reaching for moving objects \cite{7439839,Salehian-RSS-16}. By defining a controller in joint space directly, one can avoid IK and all its associated drawbacks.

Several approaches have tackled the problem of learning joint-space behaviors with task-space objectives. \cite{calinon2008probabilistic} notably attempted to address this problem by learning separate motion policies in task space and the null space of the Jacobian (which would not affect task-space position), and driving the robot with a weighted sum of the two.  However, this approach does not seek convergence to the desired task-space target and is still reliant on computing the pseudo-inverse Jacobian. \cite{calinon2010learning} and \cite{silverio2017learning} expand on this approach by projecting task-space constraints into joint space using IK, and then learning a joint-space policy that incorporates both task and joint space constraints, but this similarly relies on IK approximations and does not ensure convergence to an attractor.
% FACT-CHECK: is this what Calinon 2009 and Silverio et al. 2017 are doing? They don't ensure convergence, right? TP-GMM never seems to address it ->CORRECT
\cite{lee2014unifying} learns from demonstration in both joint and task space within the "thin-plate spline" trajectory warping framework, but does not propose a dynamical system for generating motions. \cite{hersch2008reaching} proposed an approach with similar properties to this desiderata, where two concurrent DS, one in task-space and one in joint-space, are modulated by enforcing kinematic coherence constraints to avoid singularities. The resulting DS avoids singularities through generalization of the pseudo-inverse approximations. However, because the two DS have their own unique attractors, the non-linear interaction between them imposed by the kinematic constraints does not ensure that the combined DS has a unique attractor. This gives rise to spurious attractors or cycles, and thus must be carefully tuned in order to avoid them. 
%Most recently, \cite{huang2016jointly} proposed an approach that learns a controller for playing table tennis by combining joint-space Dynamic Movement Primitives (DMP) \cite{schaal2006dynamic} to mimic a desired task-space racket swing.. \textcolor{red}{ must re-read this... I think they are doing something very similar... can remove if problematic}
% Do DMPs count as learning joint space behaviors? If yes, I'm having a hard time differentiating huang2016 from us -> Yes they do

%\subsection{Our Proposed Approach}
In this work, we seek to devise an augmented \textbf{J}oint-space \textbf{T}ask-oriented \textbf{D}ynamical \textbf{S}ystem (JT-DS) that not only incorporates task-space attractors, but also avoids the problems generated by pseudo-inverse approximations. We specifically chose to focus on linear parameter-varying dynamical systems because they are fast to compute and thus allow a controller to quickly react in a changing environment, a capability that is further improved by our not needing to compute pseudo-inverses. Our dynamical system:
\begin{enumerate}[leftmargin=*]
\item computes a \begin{bf}complex motion in joint-space\end{bf} that provably and asymptotically converges to a \begin{bf}task-space \end{bf} target.
\item \textbf{avoids} the need for computing \textbf{pseudo-inverses}, and cleanly moves through kinematic ``singularities".
\item is formulated such that complex \textbf{joint-space behaviors} can be \textbf{learned} from demonstrations in \textbf{synergy space}.
\end{enumerate}
In brief, our algorithm learns a set of \emph{behavior synergies}, each of which corresponds to a different provably stable behaviors in joint space, and modulates the use of these synergies throughout joint-space using a learned LPV system. We determine the scheduling parameters for the LPV by finding a \emph{lower-dimensional embedding} of the joint space, which accounts for the variation in the demonstrated motions, and then learning a policy in embedding space for combining our behavior synergies to accurately reconstruct the demonstrated trajectories.

The most similar approach to our proposed DS is the Jacobian transpose (JT) control \cite{wolovich1984computational} method. JT control is an inverse kinematics method that yields a dynamical system in joint space $\dot{q} = f(q)$ which converges stably over time to a desired end-effector position $x^*$, without the need for pseudo-inverse computations. It shares some of our approach's advantages: fast computation and provable task-space stability. However, despite some previous work designing velocity adjustments by hand \cite{Shi2016}, this is, to the best of our knowledge the first work to employ a JT system to learn behaviors from demonstrations. 
%while obeying the robots kinematic constraints.

This paper is organized as follows. Section \ref{Sec:Prob} formalizes the problem. The proposed dynamical system is introduced in Section \ref{Sec:DS}. In Section \ref{Sec:Learning}, a probabilistic model is introduced to approximate the parameters of the dynamical system. In addition, a convex optimization problem is  formalized to estimate these parameters. In Section \ref{Sec:Exp} we provide a thorough validation of our proposed DS and learning approach. We finalize with a discussion in Section \ref{Sec:Dis}.

%\begin{figure}[t]
%\centering
%\includegraphics[width=0.95\linewidth,trim={0 20 450 0},clip]{Pic/Schematic.jpg}
%\includegraphics[width=0.9\linewidth,trim={580 20 0 0},clip]{Pic/Schematic.jpg}
%\caption{ Standard control architecture using Cartesian dynamical systems (DS)\textbf{(top)}  and our proposed approach \textbf{(bottom)}.}
%\label{fig:schematic}
%\end{figure}
\section{Problem Statement} \label{Sec:Prob}
Consider a robotic system with $d$ task-space dimensions and $m$ degrees of freedom. We direct the system using a joint position or joint velocity controller, which can have joint position limits and a maximum joint velocity. We are further provided with a set of $N$ demonstrated joint-space trajectories $D=\{\{q_{t,n},\dot{q}_{t,n}\}_{t=1,\dots, T_n}\}_{n=1,\dots,N}$, where $T_n$ is the number of the sample points of the $n^{\text{th}}$ demonstration. We refer to the system's joint-space position as $q=\begin{bmatrix} q^1 & \dots & q^m
\end{bmatrix}^T \in \mathbb{R}^m$, and to its task-space position as $x\in \mathbb{R}^d$.\footnote{For sake of brevity and simplicity, the time index, $t$, is dropped throughout the paper. } The kinematics of the robot are assumed to be known, hence, the robot's forward kinematics is indicated by $x = H(q)$ and its Jacobian is $J(q) = \frac{dx}{dq}\in \mathbb{R}^{m\times d}$.\\
We wish to formulate a dynamical system $\dot{q} = f(q)$ which satisfies the following two criteria:
\renewcommand{\labelenumi}{(\Roman{enumi})}
\begin{enumerate}
\item The dynamical system must be asymptotically stable\footnote{Unless otherwise specified, "stability" in this paper always refers to asymptotic stability within the workspace of the robot, and assumes no joint limits. We make no claim to proving global asymptotic stability, which is in fact impossible to achieve in a joint-constrained kinematic system.} with respect to a fixed task-space target $x^*$. This can be expressed by ensuring that the following Lyapunov function
\begin{equation}
V(q) = (H(q) - x^*)^TP(H(q) - x^*) 
\label{eq:Lyp}
\end{equation}
is stable; i.e. $\dot{V}(q)<0 ~\forall q\in Q$ and $V(q)=0~ \forall q\in Q^*$. Where  $Q=\{q|q^i_{min} < q^i < q^i_{max},~\forall i\in \{1,\dots,d\}\}$ and $Q^*=\{q|H(q)=x^*\wedge q\in Q\}$. $P\in \mathbb{R}^{d\times d} $ is a symmetric and positive definite matrix. $V(.)$ can be thought of as a metric for the task-space distance-to-go.
\item The dynamical system should encapsulate the desired joint-space behaviors such that the following metric is minimized
\begin{equation}
\vspace{-5pt}
e_{total} = \frac{1}{NT_n}\sum_{n=1}^N\sum_{t=0}^{T_n} \left \| \dot{q}_{d; t,n} - f(q_{t,n}) \right \|
\label{eq:optim_error}
\end{equation}
  where $\dot{q}_d$ is the desired ``true" velocity, and $f(\cdot)$ is the motion generation policy.
\end{enumerate}

%Lastly, we wish to capture joint-space behaviors in our dynamical system.
We make two decisions by the choice of behavior error metric \eqref{eq:optim_error}. First, the metric implicitly suggests that behaviors are defined by expert motions of the behavior, and that fulfilling a behavior means moving similarly to the experts' motion. Second, the type of feature of the trajectory that is being minimized is important. If instead the error feature were joint position distance $\sum_i\left \| q_{d,i} - q_i \right \|$ where $q_d$ is a vector of demonstrated positions, then executing a "behavior" would imply mimicking position, but not velocity. Alternatively, if the error feature were joint velocity direction $\sum_i \left | \frac{\dot{q}_{d,i}}{\left \| \dot{q}_{d,i} \right \|} - \frac{\dot{q}_i}{\left \| \dot{q}_i \right \|} \right |$ mimicking a "behavior" would involve following the motion profile, but not the motion's speed (so for example a slap and a push would exhibit the same behavior). By choosing the combined direction and magnitude of the joint velocity as the error, we are choosing to mimic the magnitude and direction of the motion, which \cite{gielniak2010stylized} suggests is visually most similar to the human definition of "joint motion style".
\section{Augmented \textbf{J}oint-Space \textbf{T}ask-oriented \textbf{D}ynamical \textbf{S}ystem} \label{Sec:DS}
\label{sec:proposed_system}
We propose the following augmented Joint-space Task-oriented Dynamical System (JTDS) to achieve the two criteria presented in \eqref{eq:Lyp} and \eqref{eq:optim_error}.
\begin{equation}
\label{eq:ds}
\dot{q} = f(q) = -\mathcal{A}(q)J^T(q)P(H(q) - x^*)
\end{equation}
where $P\in \mathbb{R}^{d\times d}$, and $\mathcal{A}(q)\in \mathbb{R}^{m\times m}$ is constructed using the Linear Parameter Varying system paradigm \cite{emedi2016fixed,7439839}, where the overall $\mathcal{A}(q)$ is a changing linear combination of constant  matrices, each of which encodes a local joint-space synergy. 
\begin{equation}
\label{eq:A_def}
\mathcal{A}(q) = \sum_{k=1}^{K}\theta_k(q)A_k 
\end{equation}
where $A_k\in \mathbb{R}^{m\times m} $ are the different synergies and $\theta_k(q)\in \mathbb{R}^{1}~\forall k\in\{1,\dots,K\} $ are the scheduling parameters\footnote{The scheduling parameters can be a function of time $t$, the states of the
system $q $ or external signals $d(t)$, i.e. $\theta_k (t, q(t), d(t))$. In this paper, we only consider it as a function of the states of the system. It is noteworthy that the presented stability proof can easily be extended for $\theta_k (t, q(t), d(t))$.} modulating each local synergy through time as well as space. Based on \eqref{eq:ds}, one can utilize different synergies in different regions, and compose them to create a more complex multi-behavior motion.

Before proving that the proposed dynamical system satisfies all of the criteria, let us establish an intuitive understanding of the components of the system. While it may seem daunting at first, each of the elements has a straightforward explanation. One can intuitively understand the control law as follows: $(H(q) - x^*)$ denotes the position error w.r.t. the task target (warped according to P), and by multiplying that error by the transposed Jacobian $J^T(q)$, the error is projected into joint space (similar to Jacobian transpose control \cite{wolovich1984computational,sciavicco1988solution}). The positive definite matrix $\mathcal{A}(q)$ warps the resulting joint-space velocity; Fig. \ref{fig:A_example} illustrates the effects of  $\mathcal{A}(q)$ on the generated motion. Thus the controller can be thought of as a proportional controller in joint space. Lastly, we refer to the $P$ matrix as the \begin{bf} task augmentation matrix \end{bf}(as it augments the task error, and thus the direction of motion) and $\mathcal{A}(q)$ as the \begin{bf} joint augmentation matrix \end{bf} (as it augments the outputted joint velocities).
%When using each of these matrices, the controller will augment the joint velocities to favor using one joint more than the others (in $A_1$ the hip, in $A_2$ the knee, and in $A_3$ the ankle). This ''augmentation" is simply a matrix multiplication ($A\dot{q}_{raw}$). The components of the outputted velocity are linear combinations of the ''raw" un-augmented joint velocities, where the entries in $A$ define the precise ratios. We can see the joint positions resulting from our experiment over time on the right side of Fig. \ref{fig:A_example}. Each motion tends to use its ``primary" joint most (the joint where the velocity is heavily scaled up) and uses the other available joints to compensate for what the primary joint cannot do. For example, Motion 1 starts out using mostly the hip, but once moving the hip no longer brings the system closer to the goal, the system uses the other joints to fold inwards and reach the goal. Ultimately, all three controllers converge on their target, but each has a different path through joint space depending on which joints we choose to emphasize in the behavior matrix $A$. The off-diagonal terms of $A$ have a more nuanced contribution; e.g. $A_{1,2}$ defines the amount that elbow velocity should be converted into hip velocity.

\begin{figure}[t]
\centering
\includegraphics[width=\linewidth]{Pic/A_comparison_positions.pdf}
\caption{Three example 3-DOF motions (A, B, C), each with a different constant joint augmentation matrix $\mathcal{A}(q)$ (emphasizing the hip, knee, and ankle respectively), A: $\mathcal{A}(q)=diag(5,1,1) $, B: $\mathcal{A}(q)=diag(1,5,1)$, and C: $\mathcal{A}(q)=diag(1,1,5)$. On the left, the task-space traces of each motion. On the right, the time-scaled joint positions of each joint. Each motion tends to use its ``primary" joint most and uses the other available joints to compensate for what the primary joint cannot do.}
\label{fig:A_example}
\vspace{-15pt}
\end{figure}s

@@

%By learning a position-dependent joint augmentation matrix $\mathcal{A}(q)$, we are able to execute the joint behaviors discussed earlier by augment the relative velocities of our joints. \eqref{eq:A_def} constructs our overall $\mathcal{A}(q)$ as a linear combination of $A_k~\forall k\in\{1,\dots,K\}$ (each weighted by $\theta_k(q)$), where one can enforce different local joint behaviors in different regions, and compose them to create a more complex multi-behavior motion. In this paper the joint behavior matrix $\mathcal{A}(q)$ is determined using only the joint position $q$, though one could potentially use other information such as joint velocity $\dot{q}$, environment force or target task position $x^*$.\\

\section{Learning \textbf{J}oint-Space \textbf{T}ask-oriented \textbf{D}ynamical \textbf{S}ystem in Synergy Space} 
\label{Sec:Learning}
